Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-03-09 introduction.tex
finished figure 1

Northern Iran houses about 41 percent (32 million) of the total population of the country in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Orumieh, Rasht, and Ardabil. This region has suffered the devastating effects of earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}. Due to its importance, northern Iran has recently been the subject of various efforts to better characterize seismic hazard in the region \citep[e.g.,][]{Abdollahzadeh2014a, Boostan2015}. Among other things, these studies have highlighted the prevailing differences between different studies, the importance of quantifying uncertainties, and the need for considering all potential faults in the region---even if believed inactive---by adopting new methodologies and the latest available data.

>>>>

Northern Iran houses about 41 percent (32 million) of the total population of the country in the cities of Tehran, Mashhad, Tabriz, Karaj, Qom, Urmia, Rasht, and Ardabil. This region has suffered the devastating effects of earthquakes in the past \citep[e.g.,][]{Mehrain_1990_Tech, Chafory-Ashtiany_1999_DPM, Razzaghi_2012_Tech}. Due to its importance, northern Iran has recently been the subject of various efforts to better characterize seismic hazard in the region \citep[e.g.,][]{Abdollahzadeh2014a, Boostan2015}. Among other things, these studies have highlighted the prevailing differences between different studies, the importance of quantifying uncertainties, and the need for considering all potential faults in the region---even if believed inactive---by adopting new methodologies and the latest available data.
